---
title: "About this site"
description: |
  Some additional details about the website
---

```{r setup, include=FALSE}
library(knitr)
library(tictoc)
knitr::opts_chunk$set()
xaringanExtra::use_panelset()
```

```{css, echo=FALSE}
.panel-tab {
  flex: 1 0 20%;
  text-align: center;
}
```

::::: {.panelset}

::: {.panel}

# Day 1 {.panel-name}

## Part 1

```{r, code=readLines("2015/01-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/01-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/01-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/01-2.R")))
toc()
```

:::

::: {.panel}

# Day 2 {.panel-name}

## Part 1

```{r, code=readLines("2015/02-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/02-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/02-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/02-2.R")))
toc()
```

:::

::: {.panel}

# Day 3 {.panel-name}

## Part 1

```{r, code=readLines("2015/03-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/03-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/03-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/03-2.R")))
toc()
```

:::

::: {.panel}

# Day 4 {.panel-name}

## Part 1

```{r, code=readLines("2015/04-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/04-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/04-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/04-2.R")))
toc()
```

:::

::: {.panel}

# Day 5 {.panel-name}

## Part 1

```{r, code=readLines("2015/05-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/05-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/05-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/05-2.R")))
toc()
```

:::

::: {.panel}

# Day 6 {.panel-name}

## Part 1

```{r, code=readLines("2015/06-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/06-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/06-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/06-2.R")))
toc()
```

:::

::: {.panel}

# Day 7 {.panel-name}

## Part 1

```{r, code=readLines("2015/07-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/07-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/07-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/07-2.R")))
toc()
```

:::

::: {.panel}

# Day 8 {.panel-name}

## Part 1

```{r, code=readLines("2015/08-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/08-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/08-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/08-2.R")))
toc()
```

:::

::: {.panel}

# Day 9 {.panel-name}

## Part 1

```{r, code=readLines("2015/09-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/09-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/09-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/09-2.R")))
toc()
```

:::

::: {.panel}

# Day 10 {.panel-name}

## Part 1

```{r, code=readLines("2015/10-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/10-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2015/10-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/10-2.R")))
toc()
```

:::

::: {.panel}

# Day 11 {.panel-name}

## Part 1

```{r, code=readLines("2015/11-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/11-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/11-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/11-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 12 {.panel-name}

## Part 1

```{r, code=readLines("2015/12-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/12-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/12-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/12-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 13 {.panel-name}

## Part 1

```{r, code=readLines("2015/13-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/13-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/13-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/13-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 14 {.panel-name}

## Part 1

```{r, code=readLines("2015/14-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/14-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/14-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/14-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 15 {.panel-name}

## Part 1

```{r, code=readLines("2015/15-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/15-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/15-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/15-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 16 {.panel-name}

## Part 1

```{r, code=readLines("2015/16-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/16-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/16-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/16-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 17 {.panel-name}

## Part 1

```{r, code=readLines("2015/17-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/17-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/17-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/17-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 18 {.panel-name}

## Part 1

```{r, code=readLines("2015/18-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/18-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/18-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/18-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 19 {.panel-name}

## Part 1

```{r, code=readLines("2015/19-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/19-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/19-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/19-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 20 {.panel-name}

## Part 1

```{r, code=readLines("2015/20-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/20-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/20-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/20-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 21 {.panel-name}

## Part 1

```{r, code=readLines("2015/21-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/21-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/21-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/21-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 22 {.panel-name}

:::

::: {.panel}

# Day 23 {.panel-name}

## Part 1

```{r, code=readLines("2015/23-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/23-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/23-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/23-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 24 {.panel-name}

## Part 1

```{r, code=readLines("2015/24-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/24-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2015/24-2.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/24-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 25 {.panel-name}

## Part 1

```{r, code=readLines("2015/25-1.R"), eval=FALSE}
```

```{r, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2015/25-1.R"))) 
toc()
```

:::

:::::
