---
title: "My 2016 Solutions"
---

```{r setup, include=FALSE}
library(knitr)
library(tictoc)
knitr::opts_chunk$set()
xaringanExtra::use_panelset()
```

```{css, echo=FALSE}
.panel-tab {
  flex: 1 0 20%;
  text-align: center;
}
```

```{r, echo=FALSE}
part1 <- fs::dir_ls("2016/") |>
  stringr::str_subset("-1") |>
  stringr::str_sub(6, 7) |>
  as.numeric()

part2 <- fs::dir_ls("2016/") |>
  stringr::str_subset("-2") |>
  stringr::str_sub(6, 7) |>
  as.numeric()

one_done <- setdiff(setdiff(1:25, part2), setdiff(1:25, part1))
none_done <- intersect(setdiff(1:25, part2), setdiff(1:25, part1))

htmltools::tags$style(
  paste0(collapse = "\n",
    c(
      glue::glue(
        "#panelset_day-[one_done] {color: #EBB626 !important;}",
        .open = "[", .close = "]"
      ),
      glue::glue(
        "#panelset_day-[none_done] {color: #D63131 !important;}",
        .open = "[", .close = "]"
      )
    )
  )
)
```

::::: {.panelset}

::: {.panel}

# Day 1 {.panel-name}

## Part 1

```{r, code=readLines("2016/01-1.R"), eval=FALSE}
```

```{r day01part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/01-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/01-2.R"), eval=FALSE}
```

```{r day01part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/01-2.R")))
toc()
```

:::

::: {.panel}

# Day 2 {.panel-name}

## Part 1

```{r, code=readLines("2016/02-1.R"), eval=FALSE}
```

```{r day02part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/02-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/02-2.R"), eval=FALSE}
```

```{r day02part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/02-2.R")))
toc()
```

:::

::: {.panel}

# Day 3 {.panel-name}

## Part 1

```{r, code=readLines("2016/03-1.R"), eval=FALSE}
```

```{r day03part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/03-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/03-2.R"), eval=FALSE}
```

```{r day03part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/03-2.R")))
toc()
```

:::

::: {.panel}

# Day 4 {.panel-name}

## Part 1

```{r, code=readLines("2016/04-1.R"), eval=FALSE}
```

```{r day04part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/04-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/04-2.R"), eval=FALSE}
```

```{r day04part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/04-2.R")))
toc()
```

:::

::: {.panel}

# Day 5 {.panel-name}

## Part 1

```{r, code=readLines("2016/05-1.R"), eval=FALSE}
```

```{r day05part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/05-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/05-2.R"), eval=FALSE}
```

```{r day05part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/05-2.R")))
toc()
```

:::

::: {.panel}

# Day 6 {.panel-name}

## Part 1

```{r, code=readLines("2016/06-1.R"), eval=FALSE}
```

```{r day06part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/06-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/06-2.R"), eval=FALSE}
```

```{r day06part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/06-2.R")))
toc()
```

:::

::: {.panel}

# Day 7 {.panel-name}

## Part 1

```{r, code=readLines("2016/07-1.R"), eval=FALSE}
```

```{r day07part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/07-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/07-2.R"), eval=FALSE}
```

```{r day07part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/07-2.R")))
toc()
```

:::

::: {.panel}

# Day 8 {.panel-name}

## Part 1

```{r, code=readLines("2016/08-1.R"), eval=FALSE}
```

```{r day08part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/08-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/08-2.R"), eval=FALSE}
```

```{r day08part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/08-2.R")))
toc()
```

:::

::: {.panel}

# Day 9 {.panel-name}

## Part 1

```{r, code=readLines("2016/09-1.R"), eval=FALSE}
```

```{r day09part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/09-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/09-2.R"), eval=FALSE}
```

```{r day09part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/09-2.R")))
toc()
```

:::

::: {.panel}

# Day 10 {.panel-name}

## Part 1

```{r, code=readLines("2016/10-1.R"), eval=FALSE}
```

```{r day10part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/10-1.R")))
toc()
```

## Part 2

```{r, code=readLines("2016/10-2.R"), eval=FALSE}
```

```{r day10part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/10-2.R")))
toc()
```

:::

::: {.panel}

# Day 11 {.panel-name}

:::

::: {.panel}

# Day 12 {.panel-name}

## Part 1

```{r, code=readLines("2016/12-1.R"), eval=FALSE}
```

```{r day12part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/12-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2016/12-2.R"), eval=FALSE}
```

```{r day12part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/12-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 13 {.panel-name}

## Part 1

```{r, code=readLines("2016/13-1.R"), eval=FALSE}
```

```{r day13part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/13-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2016/13-2.R"), eval=FALSE}
```

```{r day13part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/13-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 14 {.panel-name}

## Part 1

```{r, code=readLines("2016/14-1.R"), eval=FALSE}
```

```{r day14part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/14-1.R"))) 
toc()
```

## Part 2

:::

::: {.panel}

# Day 15 {.panel-name}

## Part 1

```{r, code=readLines("2016/15-1.R"), eval=FALSE}
```

```{r day15part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/15-1.R"))) 
toc()
```

## Part 2

:::

::: {.panel}

# Day 16 {.panel-name}

## Part 1

```{r, code=readLines("2016/16-1.R"), eval=FALSE}
```

```{r day16part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/16-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2016/16-2.R"), eval=FALSE}
```

```{r day16part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/16-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 17 {.panel-name}

:::

::: {.panel}

# Day 18 {.panel-name}

## Part 1

```{r, code=readLines("2016/18-1.R"), eval=FALSE}
```

```{r day18part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/18-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2016/18-2.R"), eval=FALSE}
```

```{r day18part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/18-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 19 {.panel-name}

## Part 1

```{r, code=readLines("2016/19-1.R"), eval=FALSE}
```

```{r day19part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/19-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2016/19-2.R"), eval=FALSE}
```

```{r day19part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/19-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 20 {.panel-name}

## Part 1

```{r, code=readLines("2016/20-1.R"), eval=FALSE}
```

```{r day20part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/20-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2016/20-2.R"), eval=FALSE}
```

```{r day20part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/20-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 21 {.panel-name}

## Part 1

```{r, code=readLines("2016/21-1.R"), eval=FALSE}
```

```{r day21part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/21-1.R"))) 
toc()
```

## Part 2

```{r, code=readLines("2016/21-2.R"), eval=FALSE}
```

```{r day21part2, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/21-2.R"))) 
toc()
```

:::

::: {.panel}

# Day 22 {.panel-name}

## Part 1

```{r, code=readLines("2016/22-1.R"), eval=FALSE}
```

```{r day22part1, echo=FALSE, cache=TRUE}
tic()
eval(parse(text = readLines("2016/22-1.R"))) 
toc()
```

:::

::: {.panel}

# Day 23 {.panel-name}

:::

::: {.panel}

# Day 24 {.panel-name}

:::

::: {.panel}

# Day 25 {.panel-name}

:::

:::::
