---
title: "2020 AoC Rstats solutions"
description: |
  My solutions to the Advent of Code coding challanges.
output:
  html_document:
    toc: true
    toc_depth: 1
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
library(tidyverse)
library(magrittr)
```

My rules:

- I'm here to have fun, some solutions may not be the most efficient but they will get the answer.  
- I will use purrr `map`s and stringr functions even if I label an answer as base.

# Day 1

## Part 1

### tidyverse

```{r}
library(tidyverse)

input <- as.numeric(readLines("2020/01-input"))

expand_grid(x = input, y = input) %>%
  filter(x + y == 2020) %>%
  mutate(res = x * y) %>%
  slice(1) %>%
  pull(res)
```

### base

```{r}
input <- as.numeric(readLines("2020/01-input"))

sum2 <- function(input, target) {
  for (i in input) {
    for (j in input) {
      if (i + j == target) {
        return(i * j)
      }
    }
  }
}

sum2(input, 2020)
```

## Part 2

### tidyverse

```{r}
expand_grid(x = input, y = input, z = input) %>%
  filter(x + y + z == 2020) %>%
  mutate(res = x * y * z) %>%
  slice(1) %>%
  pull(res)
```

### base

```{r}
sum3 <- function(input, target) {
  for (i in input) {
    for (j in input) {
      for (l in input) {
        if (i + j + l == target) {
          return(i * j * l)
        }
      }
    }
  }
}

sum3(input, 2020)
```

# Day 2

## Part 1

### base

```{r}
library(purrr)
library(stringr)

input <- readLines("2020/02-input")

password_check <- function(x) {
  numbers <- as.numeric(str_extract_all(x, "[0-9]+")[[1]])
  chars <- str_extract_all(x, "[a-z]+")[[1]]
  
  count <- str_count(chars[2], chars[1])
  (numbers[1] <= count) & (numbers[2] >= count) 
}

sum(map_lgl(input, password_check))
```

## Part 2

### base

```{r}
library(purrr)
library(stringr)

input <- readLines("2020/02-input")

password_check_2 <- function(x) {
  numbers <- as.numeric(str_extract_all(x, "[0-9]+")[[1]])
  chars <- str_extract_all(x, "[a-z]+")[[1]]
  
  loc1 <- str_sub(chars[2], numbers[1], numbers[1])
  loc2 <- str_sub(chars[2], numbers[2], numbers[2])
     
  sum(loc1 == chars[1], loc2 == chars[1]) == 1
  
}

sum(map_lgl(input, password_check_2))
```

# Day 3

## Part 1

```{r}
library(purrr)

input <- readLines("2020/03-input")

# turn input into logical matrix
mat <- strsplit(input, "") %>%
  map(~.x == "#") %>%
  reduce(rbind)

traverse <- function(mat, right, down) {
  x <- y <- 1
  
  height <- nrow(mat)
  width <- ncol(mat)
  
  # Check tree collision
  trees <- 0
  repeat {
    y <- y + down
    x <- (x + right) %% width
    x <- ifelse(x == 0, width, x)
    trees <- trees + mat[y, x]
    if (y >= height) break
  }
  trees
}

traverse(mat, 3, 1)
```

## Part 2

```{r}
prod(
  traverse(mat, 1, 1),
  traverse(mat, 3, 1),
  traverse(mat, 5, 1),
  traverse(mat, 7, 1),
  traverse(mat, 1, 2)
)
```

# Day 4

This is the first day this where where we have to type a lot to get the results.

## Part 1

The first part isn't terrible long.
the input looks something like this:

```{text, eval=FALSE}
ecl:gry pid:860033327 eyr:2020 hcl:#fffffd
byr:1937 iyr:2017 cid:147 hgt:183cm

iyr:2013 ecl:amb cid:350 eyr:2023 pid:028048884
hcl:#cfa07d byr:1929

hcl:#ae17e1 iyr:2013
eyr:2024
ecl:brn pid:760753108 byr:1931
hgt:179cm

hcl:#cfa07d eyr:2025 pid:166559648
iyr:2011 ecl:brn hgt:59in
```

passports are separated by newlines, and each passport contains a number of key-value pairs. 
The task in part one is to make sure that the following fields are present in a passport:

- `byr` (Birth Year)
- `iyr` (Issue Year)
- `eyr` (Expiration Year)
- `hgt` (Height)
- `hcl` (Hair Color)
- `ecl` (Eye Color)
- `pid` (Passport ID)
- `cid` (Country ID)

but are allowed to treat the `cid` field as optional.

I start by reading in the input as I normally do and to get the passwords I first collapses the input back into 1 string using newline characters, then I can `str_split()` to get individual passports by splitting on double newlines.

I construct a vector of all the required field names and used a combination of `%in%` and `all()` to make sure all the fields are present. 

```{r}
library(purrr)
library(stringr)
library(magrittr)

input <- readLines("2020/04-input")

passports <- str_split(paste(input, collapse = "\n"), "\n\n")[[1]]

matches <- c("byr", "iyr", "eyr", "hgt", "hcl", "ecl", "pid")

valid <- str_extract_all(passports, paste0(matches, collapse = "|")) %>%
  map_lgl(~all(matches %in% .x))

sum(valid)
```

## Part 2

Now that we detected the passport with the required fields, we are asked to validate that the values in each field are valid.

- `byr` (Birth Year) - four digits; at least `1920` and at most `2002`.
- `iyr` (Issue Year) - four digits; at least `2010` and at most `2020`.
- `eyr` (Expiration Year) - four digits; at least `2020` and at most `2030`.
- `hgt` (Height) - a number followed by either cm or in:
    - If cm, the number must be at least `150` and at most `193`.
    - If in, the number must be at least `59` and at most `76`.
- `hcl` (Hair Color) - a `#` followed by exactly six characters `0-9` or `a-f`.
- `ecl` (Eye Color) - exactly one of: `amb` `blu` `brn` `gry` `grn` `hzl` `oth`.
- `pid` (Passport ID) - a nine-digit number, including leading zeroes.
- `cid` (Country ID) - ignored, missing or not.

I have 2 thoughts right away.

- get the data in data.frame as soon as possible
- create a function for each field

`create_list()` takes passwords and returns a named list, when named lists are returned inside a `map_dfr()` then you automatically get a data.frame out.

All the check functions should be pretty self-explanatory.
`check_hgt()` you need to remember that heights without units are invalid, hence the double `if_else()`.
You need to remember `^` and `$` in `check_pid()` otherwise you can also match 10-digit numbers (like i did at first).

```{r}
create_list <- function(x) {
  x <- str_split(x, "[ \n]")[[1]]
  x_split <- str_split(x, ":")

  setNames(map(x_split, 2), map(x_split, 1))
}

password_df <- passports[valid] %>%
  map_dfr(create_list)

int <- as.integer

check_byr <- function(x) int(x) >= 1920 & int(x) <= 2002

check_iyr <- function(x) int(x) >= 2010 & int(x) <= 2020

check_eyr <- function(x) int(x) >= 2020 & int(x) <= 2030

check_hgt <- function(x) {
  value <- as.numeric(str_extract(x, "[0-9]+"))
  unit <- str_remove(x, "[0-9]+")
  
  if_else(
    unit %in% c("in", "cm"),
    if_else(
      unit == "in",
      value >= 59 & value <= 76,
      value >= 150 & value <= 193
      ),
    FALSE
  )
}

check_hcl <- function(x) {
  str_detect(x, "#[0-9a-f]{6}")
}

check_ecl <- function(x) {
  x %in% c("amb", "blu", "brn", "gry", "grn", "hzl", "oth")
}

check_pid <- function(x) {
  str_detect(x, "^[0-9]{9}$")
}

library(dplyr)

password_df %>%
  filter(
    check_hgt(hgt),
    check_byr(byr),
    check_hcl(hcl),
    check_ecl(ecl),
    check_pid(pid),
    check_iyr(iyr),
    check_eyr(eyr)
  ) %>%
  nrow()
```

# Day 5

## Part 1

```{r}
input <- readLines("2020/05-input")

input <- gsub(c("[FL]"), c("0"), input)
input <- gsub(c("[BR]"), c("1"), input)

id <- strtoi(input, base = 2)

max(id)
```

## Part 2

```{r}
setdiff(seq(min(id), max(id)), id)
```

## Part 1

```{r}
library(tidyverse)
id <- read_lines("2020/05-input") %>%
  str_replace_all(c("[FL]" = "0", "[BR]" = "1")) %>%
  strtoi(base = 2)

max(id)
```

## Part 2

```{r}
setdiff(seq(min(id), max(id)), id)
```

# Day 6

Tidyverse + tidytext

## Part 1

```{r}
library(tidyverse)
library(tidytext)

answers <- read_file("2020/06-input") %>%
  tibble(input = .) %>%
  unnest_paragraphs(text, input) %>%
  rowid_to_column("group_id") %>%
  unnest_tokens(text, text) %>%
  rowid_to_column("person_id") %>%
  unnest_characters(text, text)

answers %>%
  count(group_id, text) %>%
  nrow()
```

## Part 2

```{r}
answers %>%
  group_by(group_id) %>%
  mutate(group_size = n_distinct(person_id)) %>%
  count(group_size, text) %>%
  filter(group_size == n) %>%
  nrow()
```

# Day 7

## Part 1

```{r}
library(stringr)
input <- readLines("2020/07-input")

containing_bag <- function(x) {
  str_extract(str_subset(input, paste0(".+", x)), "^.+?bag")
}

used_bags <- c()

new_bags <- "shiny gold bag"

repeat {
  newer_bags <- unique(unlist(lapply(new_bags, containing_bag)))
  
  if (length(newer_bags) == 0) {
    used_bags <- c(used_bags, new_bags)
    break
  }
  
  used_bags <- c(used_bags, new_bags)
  
  new_bags <- setdiff(newer_bags, used_bags)
}

length(setdiff(used_bags, "shiny gold bag"))
```

## Part 2

```{r}
library(stringr)
input <- readLines("2020/07-input")

bags <- str_extract_all(input, "(?<=[0-9] ).*?bag")
number <- str_extract_all(input, "[0-9]+")
number <- lapply(number, as.integer)
names(number) <- names(bags) <- str_extract(input, "^.+?bag")

find_size <- function(x, n) {
  contains <- bags[[x]]
  if (length(contains) == 0) return(n)
  n_bags <- map2_int(contains, number[[x]], find_size)
  sum(c(n_bags, 1L) * n)
}

find_size(x = "shiny gold bag", n = 1) - 1
```

# Day 8

## Part 1

```{r}
input <- readLines("2020/08-input")

run <- function(input, part2 = FALSE) {
  len <- length(input)
  n_times <- integer(len)

  accumulator <- 0

  i <- 1

  repeat {
    x <- strsplit(input[i], " ")[[1]]
    
    n_times[i] <- n_times[i] + 1
    
    if (i > len) {
      return(accumulator)
    }
    if (n_times[i] == 2) {
      if (part2) {
        return(NA)
      } else {
        return(accumulator)
      }
    }
    
    if (x[1] == "nop") {
      i <- i + 1
    } else if (x[1] == "acc") {
      accumulator <- accumulator + readr::parse_number(x[2])
      i <- i + 1
    } else if (x[1] == "jmp") {
      i <- i + readr::parse_number(x[2])
    }
  }
}

run(input)
```

## Part 2

```{r}
library(stringr)
for (i in seq_along(input)) {
  input0 <- input
  if (str_detect(input0[i], "acc")) next

  if (str_detect(input0[i], "nop")) {
    input0[i] <- str_replace(input0[i], "nop", "jmp")
  } else {
    input0[i] <- str_replace(input0[i], "jmp", "nop")
  }
  
  res <- run(input0, part2 = TRUE)
  if(!is.na(res)) break
}
res
```

# Day 9

## Part 1

```{r}
input <- as.numeric(readLines("2020/09-input"))

i <- 1

repeat {
  sums <- colSums(combn(input[seq(i, i + 24)], 2))
  if(!any(input[i + 25] == sums)) break
  i <- i + 1
}

input[i + 25]
```

## Part 2

```{r}
input <- as.numeric(readLines("2020/09-input"))

target <- input[i + 25] # My result for Part 1

i <- 1
step <- 1

repeat {
  res <- sum(input[seq(i, i + step)])
  
  if (res == target) break
  
  if (res > target) {
    i <- i + 1
    step <- 1
    next
  }
  step <- step + 1
}

sum(range(input[seq(i, i + step)]))
```

# Day 10

## Part 1

```{r}
input <- as.integer(readLines("2020/10-input"))

res <- table(diff(sort(input)))

prod(res + 1)
```

## Part 2

```{r}
input <- sort(as.integer(readLines("2020/10-input")))

runs <- rle(c(diff(c(0, input))))
weights <- c(1, 2, 4, 7)

options(scipen = 999)
prod(weights[runs$lengths[runs$values == 1]])
```

# Day 11

## Part 1

```{r}
input <- readLines("2020/11-inpurt")

# turn input into logical matrix
mat <- strsplit(input, "") %>%
  reduce(rbind)

replace <- mat

repeat {
for (i in seq_len(nrow(mat))) {
  for (j in seq_len(ncol(mat))) {
    if (mat[i, j] == ".") next
    
    temp_mat <- mat
    temp_mat[i, j] <- ""
    
    conv <- temp_mat[seq(max(i-1, 1), min(i+1, nrow(mat))),
                     seq(max(j-1, 1), min(j+1, ncol(mat)))]
    
    
    
    if (mat[i, j] == "L") {
      if (all(conv != "#")) {
        replace[i, j] <- "#"
      }
    }
    
    if (mat[i, j] == "#") {
       if (sum(conv == "#") >= 4) {
        replace[i, j] <- "L"
      }
    }
  }
}

if (identical(mat, replace)) break

mat <- replace

}


sum(mat == "#")
```

## Part 2

```{r}
input <- readLines("2020/11-inpurt")

# turn input into logical matrix
mat <- strsplit(input, "") %>%
  reduce(rbind)

find_neighbor <- function(mat, i, j, x, y) {
  res <- "."
  i <- i + y
  j <- j + x
  while (i > 0 & j > 0 & j <= ncol(mat) & i <= nrow(mat)) {
    value <- mat[i,j]
    if (value != ".") {
      res <- value
      break
    }
    i <- i + y
    j <- j + x
  }
  res
}

find_all_neighbors <- function(mat, i, j) {
  
  up <-   find_neighbor(mat, i, j, 0, -1)
  down <- find_neighbor(mat, i, j, 0, 1)
  right <- find_neighbor(mat, i, j, -1, 0)
  left <-  find_neighbor(mat, i, j, 1, 0)
  
  upright <- find_neighbor(mat, i, j, 1, -1)
  upleft <- find_neighbor(mat, i, j, -1, -1)
  downright <- find_neighbor(mat, i, j, 1, 1)
  downleft <- find_neighbor(mat, i, j, -1, 1)

  c(up, down, right, left, upright, upleft, downright, downleft)
}

replace <- mat

repeat {
for (i in seq_len(nrow(mat))) {
  for (j in seq_len(ncol(mat))) {
    if (mat[i, j] == ".") next
    
    conv <- find_all_neighbors(mat, i, j)
    
    
    if (mat[i, j] == "L") {
      if (all(conv != "#")) {
        replace[i, j] <- "#"
      }
    }
    
    if (mat[i, j] == "#") {
       if (sum(conv == "#") >= 5) {
        replace[i, j] <- "L"
      }
    }
  }
}

if (identical(mat, replace)) break

mat <- replace
}


sum(mat == "#")
```

# Day 12

## Part 1

```{r}
input <- readLines("2020/12-input")

ship <- c(0, 0)
direction <- c(1, 0)

rotate <- function(x, phi) {
  c(x[1] * cos(phi * pi / 180) - x[2] * sin(phi * pi / 180),
    x[1] * sin(phi * pi / 180) + x[2] * cos(phi * pi / 180))
}

for (i in input) {
  value <- as.numeric(str_extract(i, "[0-9]+"))
  switch(
    substr(i, 1, 1),
    N = {ship[2] <- ship[2] + value},
    S = {ship[2] <- ship[2] - value},
    E = {ship[1] <- ship[1] + value},
    W = {ship[1] <- ship[1] - value},
    L = {direction <- rotate(direction, value)},
    R = { direction <- rotate(direction, -value)},
    F = {ship <- ship + direction * value}
  )
}

sum(abs(ship))
```

## Part 2

```{r}
input <- readLines("2020/12-input")

ship <- c(0, 0)

waypoint <- c(10, 1)

rotate <- function(x, phi) {
  c(x[1] * cos(phi * pi / 180) - x[2] * sin(phi * pi / 180),
    x[1] * sin(phi * pi / 180) + x[2] * cos(phi * pi / 180))
}

for (i in input) {
  value <- as.numeric(str_extract(i, "[0-9]+"))
  
  switch(
    substr(i, 1, 1),
    N = {waypoint[2] <- waypoint[2] + value},
    S = {waypoint[2] <- waypoint[2] - value},
    E = {waypoint[1] <- waypoint[1] + value},
    W = {waypoint[1] <- waypoint[1] - value},
    L = {waypoint <- rotate(waypoint, value)},
    R = {waypoint <- rotate(waypoint, -value)},
    F = {ship <- ship + waypoint * value}
  )
}

sum(abs(ship))
```

# Day 13

## Part 1

```{r}
input <- readLines("2020/13-input")

target <- as.integer(input[1])
ids <- as.integer(str_extract_all(input[2], "[0-9]+")[[1]])

time_past <- ceiling(target / ids) * ids
which_min <- min(time_past) == time_past

(time_past[which_min] - target) * ids[which_min]
```

## Part 2

```{r}
input <- readLines("2020/13-input")

ids <- as.numeric(str_split(input[2], ",")[[1]])
offset <- seq_along(ids) - 1
offset <- offset[!is.na(ids)]
ids <- ids[!is.na(ids)]

timestamp <- 1
step <- 1

for (i in seq_along(ids)) {
  repeat {
  if ((timestamp + offset[i]) %% ids[i] == 0) break
  timestamp <- timestamp + step
  }
  
  step <- prod(ids[seq_len(i)])
}

options(scipen = 999)
timestamp
```

# Day 14

## Part 1

```{r}
library(stringr)
intTo36 <- function(x) {
  as.character(c(rep(0, 4), rev(as.integer(intToBits(x)))))
}

`[<-.memory` <- function(x, i, value) {
  res <- intTo36(value)
  res[mask != "X"] <- mask[mask != "X"]
  x[[i]] <- res
  x
}

input <- readLines("2020/14-input")

mem <- list()
attr(mem, "class") <- "memory"

for (line in input) {
  if (grepl("^mask", line)) {
    mask <- strsplit(str_extract(line, "[X0-9]+"), "")[[1]]
    next
  } 
  eval(parse(text = line))
}

options(scipen = 999)
sum(map_dbl(mem, ~ sum(as.numeric(.x) * (2 ^ seq(35, 0)))))
```

## Part 2

```{r, eval=FALSE}
res2adresses <- function(x) {
  powers <- (2 ^ seq(35, 0))
  floating <- which(x == "X")
  float_value <- replicate(length(floating), c(TRUE, FALSE), simplify = FALSE)
  float_value <- expand.grid(float_value)
  float_value <- as.matrix(float_value) %*% powers[floating]
  float_value <- as.numeric(float_value)
  x[x == "X"] <- "0"
  find_value(x) + float_value
}

`[<-.memory` <- function(x, i, value) {
  masked_address <- intTo36(i)
  masked_address[mask != "0"] <- mask[mask != "0"]
  addresses <- res2adresses(masked_address)
  for (address in addresses) {
    x[[as.character(address)]] <- intTo36(value)
  }
  x
}

input <- readLines("2020/14-input")

mem <- list()
attr(mem, "class") <- "memory"

for (line in input) {
  if (grepl("^mask", line)) {
    mask <- strsplit(str_extract(line, "[X0-9]+"), "")[[1]]
    next
  } 
  eval(parse(text = line))
}

options(scipen = 999)
sum(map_dbl(mem, ~ sum(as.numeric(.x) * (2 ^ seq(35, 0)))))
```

```{r, include=FALSE}
knitr::knit_exit()
```

# Day 15

## Part 1

```{r}
input <- c(16,1,0,18,12,14,19)

res <- rep(-1, 2020)
res[seq_along(input)] <- input
for (i in 8:2020) {
if (sum(res == res[i- 1]) == 1) {
  res[i] <- 0
} else {
  last_calls <- which(res == res[i- 1])
  res[i] <- last_calls[length(last_calls)] - last_calls[length(last_calls) - 1]
}
}
rev(res)[1]
```

## Part 2

```{r}
tictoc::tic()
input <- c(16,1,0,18,12,14,19)

res <- rep(-1, 30000000)
res[seq_along(input)] <- input

for (i in 8:300000) {
  if (sum(res == res[i- 1]) == 1) {
    res[i] <- 0
  } else {
    last_calls <- which(res == res[i- 1])
    res[i] <- last_calls[length(last_calls)] - last_calls[length(last_calls) - 1]
  }
}

rev(res)[1]
tictoc::toc()
```


```{r}
input <- c(1,3,2)
last <- list()
for (i in seq_along(input)) {
  last[as.character(input[i])] <- i
}

res <- rep(-1, 2020)
res[seq_along(input)] <- input

for (i in seq(length(input) + 1, 2020)) {
  last_value <- as.character(res[i-1])
  last_seen <- last[last_value][[1]]
  
if (length(last_seen) < 2) {
  res[i] <- 0
  last[["0"]] <- c(last[["0"]], i)
} else {
  res[i] <- last_seen[2] - last_seen[1]
  res_char <- as.character(res[i])
  last[[res_char]] <- c(last[[res_char]][length(last[[res_char]])], i)
}
}
```

# Day 16

## Part 1

```{r}
library(tidyverse)
input <- readLines("2020/16-input")
breaks <- which(input == "")

valid_values <- input[seq(1, min(breaks) - 1)] %>%
  str_extract_all("[0-9]+") %>%
  map(as.numeric) %>%
  map(~ c(seq(.x[1], .x[2]), seq(.x[3], .x[4])))

tickets <- read.csv("2020/16-input", header = FALSE,
                    skip = which(input == "nearby tickets:"))

all_valid_values <- unlist(valid_values)

check_value <- function(x, ref) {
  map_dbl(x, ~ ifelse(.x %in% ref, NA, .x))
}

wrong <- apply(tickets, 2, check_value, all_valid_values)

sum(wrong, na.rm = TRUE)
```

## Part 2

```{r}
valid_ticket <- tickets[rowSums(!is.na(wrong)) == 0, ]

can_be <- function(x) {
  which(map_lgl(valid_values, ~all(x %in% .x)))
}

pos <- numeric(length(valid_values))

candidates <- map(valid_ticket, can_be)

repeat {
  variable_ind <- which(lengths(candidates) == 1)
  if(length(variable_ind) == 0) break
  
  ref_ind <- candidates[[variable_ind]]
  
  pos[variable_ind] <- ref_ind
  
  candidates <- map(candidates, setdiff, ref_ind)
}

my_ticket <- as.numeric(str_split(input[min(breaks) + 2], ",")[[1]])

fields <- input[seq(1, min(breaks) - 1)] %>%
  str_detect("^departure")

options(scipen = 999)
prod(my_ticket[fields[pos]])
```

# Day 17

## Part 1

```{r}
library(dplyr)
library(tidyr)
input <- readLines("2020/17-input")


start <- tibble(
  x = rep(seq(7, 14), 8),
  y = rev(rep(seq(7, 14), each = 8)),
  z = 10,
  state = strsplit(input, "") %>% unlist()
)

space <- expand_grid(x = seq(1, 20), y = seq(1, 20), z = seq(1, 20)) %>%
  left_join(start, by = c("x", "y", "z")) %>%
  mutate(state = if_else(is.na(state), ".", state)) %>%
  mutate(row = row_number())
```

```{r}
find_neighbors <- function(dat) {
  space %>%
  filter(abs(x - dat$x) <= 1, abs(y - dat$y) <= 1, abs(z - dat$z) <= 1,
         !(x == dat$x & y == dat$y & z == dat$z)) %>%
  pull(row)
}

all_neighbors <- map(seq_len(nrow(space)), ~find_neighbors(space[.x, ]))
```

```{r}
next_state <- function(x, nbs) {
  if (x == "#") {
    if (sum(nbs == "#") %in% c(2, 3)) {
      return("#")
    } else {
      return(".")
    }
  } else {
    if (sum(nbs == "#") == 3) {
      return("#")
    } else {
      return(".")
    }
  }
}

for(iter in 1:6) {
  all_neighbors_states <- map(all_neighbors, ~ space$state[.x])
  space$state <- map2_chr(space$state, all_neighbors_states, next_state)
}

table(space$state)
```

## Part 2

```{r}
library(dplyr)
library(tidyr)
input <- readLines("2020/17-input")


start <- tibble(
  x = rep(seq(7, 14), 8),
  y = rev(rep(seq(7, 14), each = 8)),
  z = 0,
  w = 0,
  state = strsplit(input, "") %>% unlist()
)

space <- expand_grid(x = seq(1, 20), 
                     y = seq(1, 20), 
                     z = seq(-6, 6), 
                     w = seq(-6, 6)) %>%
  left_join(start, by = c("x", "y", "z", "w")) %>%
  mutate(state = if_else(is.na(state), ".", state)) %>%
  mutate(row = row_number())
```

```{r}
find_neighbors <- function(dat) {
  space %>%
  filter(abs(x - dat$x) <= 1, 
         abs(y - dat$y) <= 1, 
         abs(z - dat$z) <= 1,
         abs(w - dat$w) <= 1,
         !(x == dat$x & y == dat$y & z == dat$z & w == dat$w)) %>%
  pull(row)
}

all_neighbors <- map(seq_len(nrow(space)), ~find_neighbors(space[.x, ]))
```

```{r}
next_state <- function(x, nbs) {
  if (x == "#") {
    if (sum(nbs == "#") %in% c(2, 3)) {
      return("#")
    } else {
      return(".")
    }
  } else {
    if (sum(nbs == "#") == 3) {
      return("#")
    } else {
      return(".")
    }
  }
}

for(iter in 1:6) {
  all_neighbors_states <- map(all_neighbors, ~ space$state[.x])
  space$state <- map2_chr(space$state, all_neighbors_states, next_state)
}

table(space$state)
```

# Day 18

## Part 1

```{r}
library(stringr)
library(purrr)
input <- readLines("2020/18-input")

`%+%` <- function(a, b) a + b
`%*%` <- function(a, b) a * b

eval_string <- function(x) {
  map_dbl(x, ~eval(parse(text = .x)))
}

options(scipen = 999)
input %>%
  str_replace_all(c("\\+" = "%\\+%", "\\*" = "%\\*%")) %>%
  eval_string() %>%
  sum()
```

## Part 2

```{r}
eval_string_rev <- function(x) {
  rev_env <- new.env()
  rev_env$`+` <- function(a, b) base::`*`(a, b)
  rev_env$`*` <- function(a, b) base::`+`(a, b)
  map_dbl(x, ~eval(parse(text = .x), envir = rev_env))
}

input %>%
  str_replace_all(c("\\+" = "temp", "\\*" = "+", "temp" = "*")) %>%
  eval_string_rev() %>%
  sum()
```

# Day 19

## Part 1

```{r}
input <- readLines("2020/19-input")
break_point <- which(input == "")

rules <- input[seq(1, break_point - 1)]
messages <- input[seq(break_point + 1, length(input))]

rules

```

## Part 2

```{r}

```

# Day 20

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 21

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 22

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 23

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 24

## Part 1

```{r}
input <- readLines("2020/24-input")

moves <- c(
  e = 1 + 0i,
  se = 0 - 1i,
  sw = -1 - 1i,
  w = -1 + 0i,
  nw = 0 + 1i,
  ne = 1 + 1i
)
library(stringr)
library(purrr)

flips <- input %>%
  str_extract_all("[ns]?[ew]") %>%
  map(~moves[.x]) %>%
  map(sum) %>%
  reduce(c)
  
flips %>%
  table() %>%
  {sum(. %% 2 == 1)}
```

## Part 2

```{r}
n_neighbors <- function(x, y, moves) {
  rowSums(matrix(outer(x, moves, `+`) %in% y, ncol = length(moves)))
}
black <- as.complex(names(table(flips)[table(flips) %% 2 == 1]))

for (i in 1:100) {
  stay_black <- n_neighbors(black, black, moves) == 1
  
  white_candidates <- map(black, ~.x + moves) %>%
    unlist() %>%
    unique()
  
  new_black_ind <- n_neighbors(white_candidates, black, moves) == 2
  
  new_black <- white_candidates[new_black_ind]
  
  black <- c(black[stay_black], new_black)
}

length(black)
```

# Day 25

## Part 1

```{r}

```

## Part 2

```{r}

```

