---
title: "2020 AoC Rstats solutions"
description: |
  My solutions to the Advent of Code coding challanges.
output:
  html_document:
    toc: true
    toc_depth: 1
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
library(tidyverse)
```

My rules:

- I'm here to have fun, some solutions may not be the most efficient but they will get the answer.  
- I will use purrr `map`s and stringr functions even if I label an answer as base.

# Day 1

## Part 1

### tidyverse

```{r}
library(tidyverse)

input <- as.numeric(readLines("2020/01-input"))

expand_grid(x = input, y = input) %>%
  filter(x + y == 2020) %>%
  mutate(res = x * y) %>%
  slice(1) %>%
  pull(res)
```

### base

```{r}
input <- as.numeric(readLines("2020/01-input"))

sum2 <- function(input, target) {
  for (i in input) {
    for (j in input) {
      if (i + j == target) {
        return(i * j)
      }
    }
  }
}

sum2(input, 2020)
```

## Part 2

### tidyverse

```{r}
expand_grid(x = input, y = input, z = input) %>%
  filter(x + y + z == 2020) %>%
  mutate(res = x * y * z) %>%
  slice(1) %>%
  pull(res)
```

### base

```{r}
sum3 <- function(input, target) {
  for (i in input) {
    for (j in input) {
      for (l in input) {
        if (i + j + l == target) {
          return(i * j * l)
        }
      }
    }
  }
}

sum3(input, 2020)
```

# Day 2

## Part 1

### base

```{r}
library(purrr)
library(stringr)

input <- readLines("2020/02-input")

password_check <- function(x) {
  numbers <- as.numeric(str_extract_all(x, "[0-9]+")[[1]])
  chars <- str_extract_all(x, "[a-z]+")[[1]]
  
  count <- str_count(chars[2], chars[1])
  (numbers[1] <= count) & (numbers[2] >= count) 
}

sum(map_lgl(input, password_check))
```

## Part 2

### base

```{r}
library(purrr)
library(stringr)

input <- readLines("2020/02-input")

password_check_2 <- function(x) {
  numbers <- as.numeric(str_extract_all(x, "[0-9]+")[[1]])
  chars <- str_extract_all(x, "[a-z]+")[[1]]
  
  loc1 <- str_sub(chars[2], numbers[1], numbers[1])
  loc2 <- str_sub(chars[2], numbers[2], numbers[2])
     
  sum(loc1 == chars[1], loc2 == chars[1]) == 1
  
}

sum(map_lgl(input, password_check_2))
```

```{r, include=FALSE}
knitr::knit_exit()
```

# Day 3

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 4

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 5

## Part 1

```{r}

```

## Part 2

```{r}

```


# Day 6

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 7

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 8

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 9

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 10

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 11

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 12

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 13

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 14

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 15

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 16

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 17

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 18

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 19

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 20

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 21

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 22

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 23

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 24

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 25

## Part 1

```{r}

```

## Part 2

```{r}

```

