---
title: "2020 AoC Rstats solutions"
description: |
  My solutions to the Advent of Code coding challanges.
output:
  html_document:
    toc: true
    toc_depth: 1
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
library(tidyverse)
library(magrittr)
```

My rules:

- I'm here to have fun, some solutions may not be the most efficient but they will get the answer.  
- I will use purrr `map`s and stringr functions even if I label an answer as base.

# Day 1

## Part 1

### tidyverse

```{r}
library(tidyverse)

input <- as.numeric(readLines("2020/01-input"))

expand_grid(x = input, y = input) %>%
  filter(x + y == 2020) %>%
  mutate(res = x * y) %>%
  slice(1) %>%
  pull(res)
```

### base

```{r}
input <- as.numeric(readLines("2020/01-input"))

sum2 <- function(input, target) {
  for (i in input) {
    for (j in input) {
      if (i + j == target) {
        return(i * j)
      }
    }
  }
}

sum2(input, 2020)
```

## Part 2

### tidyverse

```{r}
expand_grid(x = input, y = input, z = input) %>%
  filter(x + y + z == 2020) %>%
  mutate(res = x * y * z) %>%
  slice(1) %>%
  pull(res)
```

### base

```{r}
sum3 <- function(input, target) {
  for (i in input) {
    for (j in input) {
      for (l in input) {
        if (i + j + l == target) {
          return(i * j * l)
        }
      }
    }
  }
}

sum3(input, 2020)
```

# Day 2

## Part 1

### base

```{r}
library(purrr)
library(stringr)

input <- readLines("2020/02-input")

password_check <- function(x) {
  numbers <- as.numeric(str_extract_all(x, "[0-9]+")[[1]])
  chars <- str_extract_all(x, "[a-z]+")[[1]]
  
  count <- str_count(chars[2], chars[1])
  (numbers[1] <= count) & (numbers[2] >= count) 
}

sum(map_lgl(input, password_check))
```

## Part 2

### base

```{r}
library(purrr)
library(stringr)

input <- readLines("2020/02-input")

password_check_2 <- function(x) {
  numbers <- as.numeric(str_extract_all(x, "[0-9]+")[[1]])
  chars <- str_extract_all(x, "[a-z]+")[[1]]
  
  loc1 <- str_sub(chars[2], numbers[1], numbers[1])
  loc2 <- str_sub(chars[2], numbers[2], numbers[2])
     
  sum(loc1 == chars[1], loc2 == chars[1]) == 1
  
}

sum(map_lgl(input, password_check_2))
```

# Day 3

## Part 1

```{r}
library(purrr)

input <- readLines("2020/03-input")

# turn input into logical matrix
mat <- strsplit(input, "") %>%
  map(~.x == "#") %>%
  reduce(rbind)

traverse <- function(mat, right, down) {
  x <- y <- 1
  
  height <- nrow(mat)
  width <- ncol(mat)
  
  # Check tree collision
  trees <- 0
  repeat {
    y <- y + down
    x <- (x + right) %% width
    x <- ifelse(x == 0, width, x)
    trees <- trees + mat[y, x]
    if (y >= height) break
  }
  trees
}

traverse(mat, 3, 1)
```

## Part 2

```{r}
prod(
  traverse(mat, 1, 1),
  traverse(mat, 3, 1),
  traverse(mat, 5, 1),
  traverse(mat, 7, 1),
  traverse(mat, 1, 2)
)
```

# Day 4

This is the first day this where where we have to type a lot to get the results.

## Part 1

The first part isn't terrible long.
the input looks something like this:

```{text, eval=FALSE}
ecl:gry pid:860033327 eyr:2020 hcl:#fffffd
byr:1937 iyr:2017 cid:147 hgt:183cm

iyr:2013 ecl:amb cid:350 eyr:2023 pid:028048884
hcl:#cfa07d byr:1929

hcl:#ae17e1 iyr:2013
eyr:2024
ecl:brn pid:760753108 byr:1931
hgt:179cm

hcl:#cfa07d eyr:2025 pid:166559648
iyr:2011 ecl:brn hgt:59in
```

passports are separated by newlines, and each passport contains a number of key-value pairs. 
The task in part one is to make sure that the following fields are present in a passport:

- `byr` (Birth Year)
- `iyr` (Issue Year)
- `eyr` (Expiration Year)
- `hgt` (Height)
- `hcl` (Hair Color)
- `ecl` (Eye Color)
- `pid` (Passport ID)
- `cid` (Country ID)

but are allowed to treat the `cid` field as optional.

I start by reading in the input as I normally do and to get the passwords I first collapses the input back into 1 string using newline characters, then I can `str_split()` to get individual passports by splitting on double newlines.

I construct a vector of all the required field names and used a combination of `%in%` and `all()` to make sure all the fields are present. 

```{r}
library(purrr)
library(stringr)
library(magrittr)

input <- readLines("2020/04-input")

passports <- str_split(paste(input, collapse = "\n"), "\n\n")[[1]]

matches <- c("byr", "iyr", "eyr", "hgt", "hcl", "ecl", "pid")

valid <- str_extract_all(passports, paste0(matches, collapse = "|")) %>%
  map_lgl(~all(matches %in% .x))

sum(valid)
```

## Part 2

Now that we detected the passport with the required fields, we are asked to validate that the values in each field are valid.

- `byr` (Birth Year) - four digits; at least `1920` and at most `2002`.
- `iyr` (Issue Year) - four digits; at least `2010` and at most `2020`.
- `eyr` (Expiration Year) - four digits; at least `2020` and at most `2030`.
- `hgt` (Height) - a number followed by either cm or in:
    - If cm, the number must be at least `150` and at most `193`.
    - If in, the number must be at least `59` and at most `76`.
- `hcl` (Hair Color) - a `#` followed by exactly six characters `0-9` or `a-f`.
- `ecl` (Eye Color) - exactly one of: `amb` `blu` `brn` `gry` `grn` `hzl` `oth`.
- `pid` (Passport ID) - a nine-digit number, including leading zeroes.
- `cid` (Country ID) - ignored, missing or not.

I have 2 thoughts right away.

- get the data in data.frame as soon as possible
- create a function for each field

`create_list()` takes passwords and returns a named list, when named lists are returned inside a `map_dfr()` then you automatically get a data.frame out.

All the check functions should be pretty self-explanatory.
`check_hgt()` you need to remember that heights without units are invalid, hence the double `if_else()`.
You need to remember `^` and `$` in `check_pid()` otherwise you can also match 10-digit numbers (like i did at first).

```{r}
create_list <- function(x) {
  x <- str_split(x, "[ \n]")[[1]]
  x_split <- str_split(x, ":")

  setNames(map(x_split, 2), map(x_split, 1))
}

password_df <- passports[valid] %>%
  map_dfr(create_list)

int <- as.integer

check_byr <- function(x) int(x) >= 1920 & int(x) <= 2002

check_iyr <- function(x) int(x) >= 2010 & int(x) <= 2020

check_eyr <- function(x) int(x) >= 2020 & int(x) <= 2030

check_hgt <- function(x) {
  value <- as.numeric(str_extract(x, "[0-9]+"))
  unit <- str_remove(x, "[0-9]+")
  
  if_else(
    unit %in% c("in", "cm"),
    if_else(
      unit == "in",
      value >= 59 & value <= 76,
      value >= 150 & value <= 193
      ),
    FALSE
  )
}

check_hcl <- function(x) {
  str_detect(x, "#[0-9a-f]{6}")
}

check_ecl <- function(x) {
  x %in% c("amb", "blu", "brn", "gry", "grn", "hzl", "oth")
}

check_pid <- function(x) {
  str_detect(x, "^[0-9]{9}$")
}

library(dplyr)

password_df %>%
  filter(
    check_hgt(hgt),
    check_byr(byr),
    check_hcl(hcl),
    check_ecl(ecl),
    check_pid(pid),
    check_iyr(iyr),
    check_eyr(eyr)
  ) %>%
  nrow()
```

```{r, include=FALSE}
knitr::knit_exit()
```

# Day 5

## Part 1

```{r}

```

## Part 2

```{r}

```


# Day 6

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 7

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 8

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 9

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 10

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 11

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 12

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 13

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 14

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 15

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 16

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 17

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 18

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 19

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 20

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 21

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 22

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 23

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 24

## Part 1

```{r}

```

## Part 2

```{r}

```

# Day 25

## Part 1

```{r}

```

## Part 2

```{r}

```

