---
title: "R Advent Of Code"
description: |
  Emil Hvitfeldt's solutions
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

This website is created using the [emilhvitfeldt/rstats-adventofcode](https://github.com/emilhvitfeldt/rstats-adventofcode) repository. I try to save all my solution in one place here.

I don't have any rules I follow. I will end up doing most solutions using base R because of the nature of the problems. I will be using both `purrr` and `stringr` when the need comes up, I don't hate myself. I'm here to write code and have fun doing it.

# Completion

```{css}
tbody {
  color: #ffff66;
}

thead {
  color: #cccccc;
}
```

```{r}
#| message: false
library(tidyverse)

get_solutions <- function(year) {
  res <- glue::glue("{year}/") |>
  fs::dir_ls() |>
  stringr::str_subset("input", negate = TRUE) |>
  basename() |>
  stringr::str_sub(1, 2) |>
  as.numeric() |>
  factor(levels = 1:25)
  
  tibble(Day = res, year = year)
}

years <- 2015:2025

years %>%
  map_dfr(get_solutions) %>%
  mutate(year = factor(year, years)) %>%
  count(year, Day, .drop = FALSE) %>%
  group_by(year) %>%
  mutate(n = case_when(
    Day != 25 ~ n,
    sum(n) == 49 ~ 2L,
    TRUE ~ n
  )) %>%
  mutate( n = strrep("*", n)) %>%
  pivot_wider(names_from = year, values_from = n) %>%
  knitr::kable()
```

